Endogenous Politics and \\ the Design of Trade Institutions

### 2018-03-02 presentation.tex
UNL presentation with pauses

%\documentclass{beamer} 
\documentclass[handout]{beamer} 
\usetheme{Ilmenau}
\usepackage{graphicx,verbatim,hyperref}
\usepackage{textpos}

@@

	\item If lobbying effort subtracted as cost from $W$, welfare no longer monotonic in $\ga$
	\pause
		\begin{itemize}
			\item If weights must sum to 1, welfare also not monotonic in $\ga$
		\end{itemize}
\end{itemize}
\end{frame}

@@

\begin{frame}{Comparison to the Literature}
Others derive non-monotonicity in lobbying effort/tariff 
\begin{itemize}
	\item Maggi $\&$ Rodriguez-Clare (1998/2007): dynamic firm investment disortions
	\item Mitra (2002): lobbies pay investment cost to form
\end{itemize}

\vskip.15in
Here, I acknowledge the gov't objective function may be fundamentally non-monotonic
\begin{itemize}
	\item Achieve same results with simpler model
	\item Endogenous politics in a wider range of questions
	\item Can have both endogenous / exogenous at the same time $\Rightarrow$ unify the exogenous and endogenous politics literatures
\end{itemize}
\end{frame}

@@

\end{itemize}
\pause
%\hyperlink{repeated<1>}{\beamergotobutton{Repeated Game Intuition}}
\end{frame}

@@

\pause
\vskip.2in

If $\ga$ is only endogenous, escape clause causes problems, provides no benefits
\end{frame}

>>>>

\documentclass{beamer} 
%\documentclass[handout]{beamer} 
\usetheme{Ilmenau}
\usepackage{graphicx,verbatim,hyperref}
\usepackage{textpos}

@@

	\item If lobbying effort subtracted as cost from $W$, welfare no longer monotonic in $\ga$
		\begin{itemize}
			\item If weights must sum to 1, welfare also not monotonic in $\ga$
		\end{itemize}
\end{itemize}
\end{frame}

@@

\begin{frame}{Comparison to the Literature}
\pause
Others derive non-monotonicity in lobbying effort/tariff 
\pause
\begin{itemize}
	\item Maggi $\&$ Rodriguez-Clare (1998/2007): dynamic firm investment disortions
	\pause
	\item Mitra (2002): lobbies pay investment cost to form
\end{itemize}

\vskip.15in
\pause
Here, I acknowledge the gov't objective function may be fundamentally non-monotonic
\pause
\begin{itemize}[<+->]
	\item Achieve same results with simpler model
	\item Endogenous politics in a wider range of questions
	\item Can have both endogenous / exogenous at the same time $\Rightarrow$ unify the exogenous and endogenous politics literatures
\end{itemize}
\end{frame}

@@

\end{itemize}
%\pause
%\hyperlink{repeated<1>}{\beamergotobutton{Repeated Game Intuition}}
\end{frame}

@@

\vskip.2in
\pause
If $\ga$ is only endogenous, escape clause causes problems, provides no benefits
\end{frame}
